---
title: "糖尿病 預測模型"
output: github_document
---

## 資料前處理

###資料讀取
Description: Predict the onset of diabetes in female Pima Indians from medical record data.
Type: Binary Classification
Dimensions: 768 instances, 9 attributes
Inputs: Numeric
Output: Categorical, 2 class labels

1.Number of times pregnant
2.Plasma glucose concentration a 2 hours in an oral glucose tolerance test
3.Diastolic blood pressure (mm Hg)
4.Triceps skin fold thickness (mm)
5.2-Hour serum insulin (mu U/ml)
6.Body mass index (weight in kg/(height in m)^2)
7.Diabetes pedigree function
8.Age (years)
9.Class variable (0 or 1)

diabetes: pos陽性 / neg陰性

```{r message=F,warning=F}
library(mlbench)
data(PimaIndiansDiabetes) 
str(PimaIndiansDiabetes) 
```

###將資料隨機分成訓練組與測試組

隨機將3/4的資料分到訓練組（Test==F），剩下1/4為測試組（Test==T）

```{r}

PimaIndiansDiabetesC<-PimaIndiansDiabetes[complete.cases(PimaIndiansDiabetes),] 
c(nrow(PimaIndiansDiabetes),nrow(PimaIndiansDiabetesC))

PimaIndiansDiabetesC$Test<-F 

PimaIndiansDiabetesC[
    sample(1:nrow(PimaIndiansDiabetesC),nrow(PimaIndiansDiabetesC)/4),
     ]$Test<-T 

c(sum(PimaIndiansDiabetesC$Test==F),sum(PimaIndiansDiabetesC$Test==T))


```

## 預測模型建立

###模型建立

由於變數多，且多為連續變項，而輸出為二元類別變項，故選擇邏輯迴歸演算法建立模型，並使用雙向逐步選擇最佳參數組合。

```{r warning=F,message=F}
fit<-glm(diabetes~., PimaIndiansDiabetesC[PimaIndiansDiabetesC==F,],family="binomial")
library(MASS)
finalFit<-stepAIC(fit,direction = "both",trace = F)
summary(finalFit)$coefficients

```


##預測模型驗證

```{r warning=F,message=F,fig.height=4.5}
DiabetePred<-predict(finalFit,newdata = PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,])
DiabeteAns<-ifelse(DiabetePred<0.5,"pos","neg") 
DiabeteAns<-factor(DiabeteAns,levels = c("pos","neg"))
library(caret)
sensitivity(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
specificity(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
posPredValue(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)
negPredValue(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)

```

- 敏感度 `r sensitivity(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)*100`%
- 特異性 `r specificity(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)*100`%
- 陽性預測率 `r posPredValue(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)*100`%
- 陰性預測率 `r negPredValue(DiabeteAns,PimaIndiansDiabetesC[PimaIndiansDiabetesC$Test==T,]$diabetes)*100`%

